---
title: "Session 2: Homework 1"
author: "Daniel Zeiner"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
library(scales)
```



# Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alchohol consumption in different countries. The data `drinks` is available as part of the `fivethirtyeight` package. Make sure you have installed the `fivethirtyeight` package before proceeding.


```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)


# or download directly
alcohol_direct <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")

```


What are the variable types? Any missing values we should worry about? 

* No missing values 
* No dublicates
* 1 Character value and 4 numeric values 

```{r glimpse_skim_data}
# YOUR CODE GOES HERE
glimpse(alcohol_direct)
skim(alcohol_direct)
```


Make a plot that shows the top 25 beer consuming countries

```{r beer_plot}
# YOUR CODE GOES HERE
ordered_beer <- head(alcohol_direct[order(alcohol_direct$beer_servings, decreasing = TRUE),], n=25)

ordered_beer %>% ggplot(aes(y= reorder(country, beer_servings, ), x=beer_servings)) +
  geom_col() + 
  ylab("Countries") +
  xlab("Beer servings")
  

```

Make a plot that shows the top 25 wine consuming countries

```{r wine_plot}

# YOUR CODE GOES HERE
ordered_wine <- head(alcohol_direct[order(alcohol_direct$wine_servings, decreasing = TRUE),], n=25)

ordered_wine %>% ggplot(aes(y= reorder(country, wine_servings, ), x=wine_servings)) +
  geom_col() + 
  ylab("Countries") +
  xlab("Wine servings")
  

```

Finally, make a plot that shows the top 25 spirit consuming countries
```{r spirit_plot}
# YOUR CODE GOES HERE
ordered_spirit <- head(alcohol_direct[order(alcohol_direct$spirit_servings, decreasing = TRUE),], n=25)

ordered_spirit %>% ggplot(aes(y= reorder(country, spirit_servings, ), x=spirit_servings)) +
  geom_col() + 
  ylab("Countries") +
  xlab("Spirit servings")
```


